### 2024-07-25 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.rmd
rewriting based on feedback

<!-- Appendix D -->

@@

# Appendix D: Initial Coding Protocol QMP Analyses

@@

For hypothesis 5, a logistic regression model was used to test the association between the QMP ratio in replication protocols and replication success. In this appendix we run the model based on the QMP ratios obtained using the initial protocol. The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model. Appendix B already contained the results of the multilevel sensitivity models for hypothesis 5 & 6 based on the QMP ratios obtained using the revised coding protocol. In this appendix we show the result for the same models based on the QMP ratios obtained using the initial protocol.

@@

```{r Hypotheses5And6SensitivityAnalysesInitial}
## Hypothesis 5 sensitivity test using a random intercept Guassian model.
# create dummy H5 dataframe for use in sensitivity test
data_h5_sens <- data_h5

# convert outcome variable to be usable with Gaussian distribution via
# logit transform.
data_h5_sens$QMP <- log(data_h5_sens$QMP_ratio /(1 - data_h5_sens$QMP_ratio)) # TO INITIAL APPENDIX

check_h5 <- apa_print(lmer(formula = QMP ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))

## Hypothesis 6 sensitivity test using a random intercept Guassian model.
# create dummy H6 dataframe for use in sensitivity test
data_h6_sens <- data_h6

# convert outcome variable to be usable with Gaussian distribution via
# logit transform. FIRST ELEMENTS TO INITIAL APPENDIX
data_h6_sens$QMP <- log(data_h6_sens$QMP_ratio /(1 - data_h6_sens$QMP_ratio))
data_h6_sens$Rep_QMP <- log(data_h6_sens$Rep_QMP_ratio /(1 - data_h6_sens$Rep_QMP_ratio))

# running the models one with none revised QMP ratio's and one with
check_h6 <- apa_print(lmer(formula = Rep_QMP ~ 1 + QMP + (1|many_labs_version), data = data_h6_sens))

@@

@@

The bottom panel of Figure \@ref(fig:Plot456CodeInitial) already shows that original articles contained a significantly larger proportion of QMPs than replication protocols for the measures of the same effects. Beta-regression was used to test the difference in QMP ratio based on the initial protocol coding, between original articles and replication protocols. The results of this test indicated that this difference was significant (`r betareg_output_to_apa_full(H4_test_results)`). This result is similar to the result found using the revised coding protocol in line with hypothesis 4.

Contrary to the results based on the revised coding protocol, a decrease in QMP ratio based on the initial coding protocol did not significantly relate to replication success (`r H5_test_results_with_OR`). Thus, not supporting hypothesis 5.

Similarly to the previous test, the relation was not significant for the QMP ratios obtained with the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`). Thus, not supporting hypothesis 6. Figure \@ref(fig:Plot46InitialDataCode) displays this relationship visually. Table \@ref(tab:H6ExploratoryAssociationsInitialTable) shows the relations between original and replication QMP ratios for each QMP type based on the initial protocol. Figure \@ref(fig:Plot46FullInitialDataCode) shows the same relations displayed visually.

```{r Plot46InitialDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication total QMP ratios with linear regression line. Each dot in the figure describes the QMP ratio in that graph across both the original article and its replication protocol. Note: jitter was applied to these dots to show the number of observations at points where multiple dots were present"}
ggplot(plot_46_data[plot_46_data$QMP_type == "QMP.Ratio" & plot_46_data$QMP_Rep_type == "Rep.QMP.Ratio",], aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.01, height = 0.01) +
  stat_smooth(method="lm") + 
  theme_minimal() +
  theme(strip.text.y = element_text(size = 7), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
  ylab("QMP Ratio (Replication Protocol)") +
  xlab("QMP Ratio (Original Article)") 
```

@@

```{r Plot46FullInitialDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication total QMP ratios obtained using the intial coding protocol with linear regression line. Each dot in the figure describes the QMP ratio in that graph across both the original article and its replication protocol. Note: jitter was applied to these dots to show the number of observations at points where multiple dots were present"}
# Initial
ggplot(plot_46_data, aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.05, height = 0.05) +
  stat_smooth(method="lm") + 
  theme_bw() +
  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
    color = "black", fill = "white", size = 1, linetype = "solid"
  )) +
  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
  facet_grid(vars(QMP_Rep_type), vars(QMP_type))

@@

Now looking at the multilevel sensitivity analyses (see appendix B), only now using the QMP ratios based on the initial coding protocol. Contrary to the results of the multilevel sensitivity model testing hypothesis 5 using QMP ratios obtained with the revised coding protocol, the relationship in the multilevel model was no longer significant for QMP ratios obtained with the initial coding protocol (`r check_h5$full_result$hypothesis_supportTRUE`).

Similarly to the results of the multilevel sensitivity model testing hypothesis 5 using QMP ratios obtained with the revised coding protocol, the relationship in the multilevel model was not significant for QMP ratios obtained with the initial coding protocol (`r check_h6$full_result$QMP`).

>>>>

<!-- Supplementary Analyses D -->

@@

# Supplementary Analyses D: Initial Coding Protocol QMP Analyses

@@

For Hypothesis 5, a logistic regression model was used to test the association between the QMP ratio in replication protocols and replication success. In this appendix we run the model based on the QMP ratios obtained using the initial protocol. The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model. [Supplementary Analyses B](Supplementary_multilevel_analyses.Rmd) already contained the results of the multilevel sensitivity models for Hypothesis 5 & 6 based on the QMP ratios obtained using the revised coding protocol. In this appendix we show the result for the same models based on the QMP ratios obtained using the initial protocol.

@@

```{r Hypotheses5And6SensitivityAnalysesInitial}
## Hypothesis 5 sensitivity test using a random intercept and a random slope Gaussian model.
# create dummy H5 dataframe for use in sensitivity test
data_h5_sens <- data_h5

# convert outcome variable to be usable with Gaussian distribution via
# logit transform.
data_h5_sens$QMP <- log(data_h5_sens$QMP_ratio /(1 - data_h5_sens$QMP_ratio))

# running the models
random_intercept_h5_REV <- apa_print(lmer(formula = QMP ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))

random_slope_h5_REV <- apa_print(lmer(formula = QMP ~ 1 + hypothesis_support + (1+hypothesis_support|many_labs_version), data = data_h5_sens))

## Hypothesis 6 sensitivity test using a random intercept and a random slope Gaussian model.
# create dummy H6 dataframe for use in sensitivity test
data_h6_sens <- data_h6

# convert outcome variable to be usable with Gaussian distribution via
# logit transform.
data_h6_sens$QMP <- log(data_h6_sens$QMP_ratio /(1 - data_h6_sens$QMP_ratio))
data_h6_sens$Rep_QMP <- log(data_h6_sens$Rep_QMP_ratio /(1 - data_h6_sens$Rep_QMP_ratio))

# running the models one with initial QMP ratio's
random_intercept_h6_REV <- apa_print(lmer(formula = Rep_QMP ~ 1 + QMP + (1|many_labs_version), data = data_h6_sens))

random_slope_h6_REV <- apa_print(lmer(formula = Rep_QMP ~ 1 + QMP + (1+QMP|many_labs_version), data = data_h6_sens))

@@

# Using a glm to check if results differs in direction and significance from the 
# beta-regression, to check that including a linear regression line in figure 46
# is representative of the relationship.
H6_glm_test <- glm(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)

H6_glm_test_results <- apa_print(H6_glm_test)$full_result$QMP_ratio

@@

The bottom panel of Figure \@ref(fig:Plot456CodeInitial) already shows that original articles contained a significantly larger proportion of QMPs than replication protocols for the measures of the same effects. Beta-regression was used to test the difference in QMP ratio based on the initial protocol coding, between original articles and replication protocols. The results of this test indicated that this difference was significant (`r betareg_output_to_apa_full(H4_test_results)`). This result is similar to the result found using the revised coding protocol in line with Hypothesis 4.

Contrary to the results based on the revised coding protocol, a decrease in QMP ratio based on the initial coding protocol did not significantly relate to replication success (`r H5_test_results_with_OR`). Thus, not supporting Hypothesis 5.

Similarly to the previous test, the relation was not significant for the QMP ratios obtained with the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`). Thus, not supporting Hypothesis 6. Figure \@ref(fig:Plot46InitialDataCode) displays this relationship visually. Table \@ref(tab:H6ExploratoryAssociationsInitialTable) shows the relations between original and replication QMP ratios for each QMP type based on the initial protocol. Figure \@ref(fig:Plot46FullInitialDataCode) shows the same relations displayed visually.

```{r Plot46InitialDataCode, error = FALSE, warning = FALSE, fig.cap = paste0("Scatterplot of original QMP ratios and replication total QMP ratios based on the initial protocol with a linear regression line. The linear regression line is included, as the result based on linear regression was similarly in direction and significance to the beta regression used to test Hypothesis 6 (", H6_glm_test_results, "), while being easier to understand visually. Each dot in the figure describes the QMP ratio in that graph across both the original article and its replication protocol. Note: jitter was applied to these dots to show the number of observations at points where multiple dots were present.")}
ggplot(plot_46_data[plot_46_data$QMP_type == "QMP.Ratio" & plot_46_data$QMP_Rep_type == "Rep.QMP.Ratio",], aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.01, height = 0.01) +
  stat_smooth(method="lm") + 
  theme_minimal() +
  theme(strip.text.y = element_text(size = 7), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
  ylab("QMP Ratio (Replication Protocol)") +
  xlab("QMP Ratio (Original Article)")

@@

```{r Plot46FullInitialDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original QMP ratios and replication total QMP ratios obtained using the intial coding protocol with linear regression lines. Each dot in the figure describes the QMP ratio in that graph across both the original article and its replication protocol. Note: jitter was applied to these dots to show the number of observations at points where multiple dots were present"}
# Initial
ggplot(plot_46_data, aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.05, height = 0.05) +
  stat_smooth(method="lm") + 
  theme_bw() +
  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
    color = "black", fill = "white", size = 1, linetype = "solid"
  )) +
  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
  facet_grid(vars(QMP_Rep_type), vars(QMP_type))

@@

Now we look at the multilevel sensitivity analyses using the QMP ratios based on the initial coding protocol. Contrary to the results of the model presented in the main text and the random intercept model testing Hypothesis 5 using QMP ratios obtained with the revised coding protocol, the relationship in the random intercept and random slope was no longer significant for QMP ratios obtained with the initial coding protocol (random intercept: `r random_intercept_h5_REV$full_result$hypothesis_supportTRUE`; random slope: `r random_slope_h5_REV$full_result$hypothesis_supportTRUE`).

For Hypothesis 6, similarly to the results of the multilevel sensitivity analysis models testing Hypothesis 5, using QMP ratios obtained with the revised coding protocol, the relationship in both the random intercept and random slope models was not significant for QMP ratios obtained with the initial coding protocol (random intercept: `r random_intercept_h6_REV$full_result$QMP`; random slope: `r random_slope_h6_REV$full_result$QMP`).

### 2024-07-25 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_omega_analyses.rmd
rewriting based on feedback

<!-- Appendix C -->

@@

# Appendix C: Omega Coefficient Analyses

@@

### Explanation of Relevance
Omega was included since it has been argued to be a more informative measure of reliability than alpha, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing]. We focused our attention on the Cronbach’s Alpha in the main text, because Cronbach’s Alpha is used more commonly in research allowing us to make comparisons between calculated and reported reliabilities. Furthermore, we were able to calculate the standard error of alpha to be used in the Reliability Generalization meta-analysis. Omega was calculated using the omega function in the *psych* R package [@R-psych]. Default arguments were used in the function except the nfactors argument, which was set to 1.

@@

The ICC was calculated similarly based on the omega as was done for Cronbach's alpha in the article. The analysis for H3 related the calculated average reliability coefficients for each replication set to whether the replication was successful when judged at meta-significance level of $alpha <.05$. A multilevel random-intercept, and a random-slope equivalent model to the model above were also run for Omega, similarly to what was done for Cronbach's alpha in Appendix B.

@@

# well this OR is still quite a ridiculous number now..., but then again a step from 0 omega to 1, is quite a jump too...
```

@@

The calculated Omega coefficient did not significantly relate to replication success in the main logistic regression model. Similarly, non-significance was also observed in the multilevel random-intercept and random-slope models (random intercept: `r H3_test_result_int_sensitivity_omega$full_result$omega`; random slope: `r H3_test_result_slp_sensitivity_omega$full_result$omega`).

@@

Thus, no evidence for hypothesis 3 was found. However, caution in interpreting the test results is needed. The number of measures for which the omega coefficient could be and was calculated was quite low (`r apa_num(sum(!is.na(data_h3_avg$omega)), numerals = FALSE)`).

The figure below shows additional information on the distributions of the calculated omega scores and their relation to replication success. It mostly resembles Figure \@ref(fig:Plot23AlphaCode) from the article, with some studies being omitted as the omega coefficient function did not converge or run properly on those data. Furthermore, information reagrding heterogeneity was not present since the standard error of omega was not known, and comparisons between reported coefficients were omitted, since no article reported any omega coefficients.

>>>>

<!-- Supplementary Analyses C -->

@@

# Supplementary Analyses C: Omega Coefficient Analyses

@@

### Explanation of Relevance
Omega was included since it has been argued to be a more informative measure of reliability than alpha, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing]. We focused our attention on the Cronbach’s Alpha in the main text, because Cronbach’s Alpha is used more commonly in research allowing us to make comparisons between calculated and reported reliabilities. Furthermore, we were able to calculate the standard error of alpha to be used in the Reliability Generalization meta-analysis. Omega was calculated using the omega function in the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych]. Default arguments were used in the function except the nfactors argument, which was set to 1.

@@

The ICC was calculated similarly based on the omega as was done for Cronbach's alpha in the article. The analysis for H3 related the calculated average reliability coefficients for each replication set to whether the replication was successful when judged at meta-significance level of $alpha <.05$. A multilevel random-intercept, and a random-slope equivalent model to the model above were also run for Omega, similarly to what was done for Cronbach's alpha in [Supplementary Analyses B](Supplementary_multilevel_analyses.Rmd).

@@

@@

The calculated Omega coefficient did not significantly relate to replication success in the main logistic regression model. Similarly, non-significance was also observed in the multilevel random-intercept model (`r H3_test_result_int_sensitivity_omega$full_result$omega`). The random slope model did not converge.

@@

Thus, no evidence in favor of Hypothesis 3 was found. However, caution in interpreting the test results is needed. The number of measures for which the omega coefficient could be and was calculated was quite low (`r apa_num(sum(!is.na(data_h3_avg$omega)), numerals = FALSE)`).

The figure below shows additional information on the distributions of the calculated omega scores and their relation to replication success. It mostly resembles Figure \@ref(fig:Plot23AlphaCode) from the article, with some studies being omitted as the omega coefficient function did not converge or run properly on those data. Furthermore, information regarding heterogeneity was not present since the standard error of omega was not known, and comparisons between reported coefficients were omitted, since no article reported any omega coefficients.

### 2024-07-25 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd
rewriting based on feedback

<!-- Appendix A -->

@@

# Appendix A: Pre-registration Analyses

@@

This analysis was omitted from the article because it did not link well enough to hypothesis 2. The test results also do not give use a very informative representations of variance in reliability in the data for us to draw further inferences from. For instance, it assumes that we should observe large differences in reliabilities between measures for this to provide an accurate test of whether the variance within measures is large or not.

@@

For the sake of this analysis the simple heuristic was chosen that if the measure was used as a single composite variable in the analyses, then it should be uni-dimensional. This is somewhat similar to what was done by @shaw2020measurement, but for the sake of this article it was deemed to strong an assumption to make that this heuristic would always hold. For instance, IQ score is often used as a single indicator score, however the construct of IQ is not considered unidimensional, and is instead understood to have many sub-dimensions (e.g. verbal comprehension, perceptual reasoning, etc.). As a result, the use of a single score in the analyses cannot be taken as evidence that the construct is considered unidimensional by neither the authors, nor the broader literature on the topic. Nevertheless, we present here the result of the analyses made under the assumption that the one score, one dimension heuristic holds.

@@

```{r cfaResultsStoring, include = FALSE, eval = FALSE}
# storing the cfa_results, so they can be referenced within the main manuscript.
open_data(data = cfa_results, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(cfa_results))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(cfa_results))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(cfa_results))), ".yml")) 
```

@@

Follow-up analyses were preregistered for hypothesis 6. The pre-registered plan was to make use of contingency tables to compare relations between all five QMP types across original and replication studies. The goal of these analyses was to see if there are any type specific carry-over effects in QMPs between original and replication. Due to the large number of tests, the focus was exploratory using visualization rather than inference.

It is partly this large number of tests, as well as the resulting lack of clear interpretability in the results that caused this analysis to be omitted from the main article. . However, This analysis was anyhow intended not as supplementary to the main test for hypothesis 6. Furthermore, the analyses would regardless have to be changed from the pre-registered analyses to beta-regressions for each unique combination of the QMP categories across original and replication. For completeness and transparency the analyses using beta-regressions are reported here.

>>>>

<!-- Supplementary Analyses A -->

@@

# Supplementary Analyses A: Pre-registration Analyses

@@

This analysis was omitted from the article because it did not link well enough to Hypothesis 2. The test results also do not give use a very informative representations of variance in reliability in the data for us to draw further inferences from. For instance, it assumes that we should observe large differences in reliabilities between measures for this to provide an accurate test of whether the variance within measures is large or not.

@@

For the sake of this analysis the simple heuristic was chosen that if the measure was used as a single composite variable in the analyses, then it should be unidimensional. This is somewhat similar to what was done by @shaw2020measurement, but for the sake of this article it was deemed to strong an assumption to make that this heuristic would always hold. For instance, IQ score is often used as a single indicator score, however the construct of IQ is not considered unidimensional, and is instead understood to have many sub-dimensions (e.g. verbal comprehension, perceptual reasoning, etc.). As a result, the use of a single score in the analyses cannot be taken as evidence that the construct is considered unidimensional by neither the authors, nor the broader literature on the topic. Nevertheless, we present here the result of the analyses made under the assumption that the one score, one dimension heuristic holds.

@@

```{r cfaResultsStoring, include = FALSE, eval = FALSE}
# storing the cfa_results, so they can be referenced within the main manuscript. THIS DOES NOT NEED TO BE RUN FOR REPRODUCING THE RESULTS.
open_data(data = cfa_results, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(cfa_results))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(cfa_results))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(cfa_results))), ".yml")) 
```

@@

Follow-up analyses were preregistered for hypothesis 6. The pre-registered plan was to make use of contingency tables to compare relations between all five QMP types across original and replication studies. The goal of these analyses was to see if there are any type specific carry-over effects in QMPs between original and replication. Theses analyses were changed from the pre-registered analyses to beta-regressions for each unique combination of the QMP categories across original and replication, as the original analysis using contingency tables was later deemed improper for our data and hypothesis 6.

Due to the large number of tests, the focus was exploratory using visualization rather than inference. It is the large number of tests combined with the fact that our sample size was not large enough to support that number of tests that we omitted these analyses from the main text. Furthermore, this analysis was intended as supplementary to the main test for hypothesis 6, and was pre-registered as exploratory. For completeness and transparency the analyses using beta-regressions are reported here.
